\normalfont \normalsize \textsc{Northwestern University} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Masters Thesis \\ \horrule{2pt} \\[0.5cm]

### 2016-08-28 Gradschool/thesis/final/chap2.tex
expanded implementation chapter, merged bayesian statistics and GR chapter, relegated GR derivation to appendix

Where $\vec{X}$ and $\vec{Y}$ are the wave-frame axes. These can be redefined in terms of the working parameters as

\begin{align}
\text{PUT DEFINITIONS HERE}
\end{align}

Our objective is to produce this quantity for a group of samples, all at once, as a coherent vectorized operation. One a sample-to-sample basis, the numbers that vary are the components of the vectors $\vec{X}$ and $\vec{Y}$. Thus we need a function that takes as input a \textit{list} vectors (or \textit{vector}) of vectors and produces a vector with the right components as output. To that end we define the tensor $X^{i}_{j}$ where

@@

>>>>

Where $\vec{X}$ and $\vec{Y}$ are the wave-frame axes. These can be redefined \cite{antennafacdefn} in terms of the working parameters as

\begin{align}
\vec{X} &=
\begin{bmatrix}
-\cos(\psi)\sin(h) - \sin(\psi)\cos(h)\sin(\delta) \\
-\cos(\psi)\cos(h) + \sin(\psi)\sin(h)\sin(\delta) \\
\sin(\psi)\cos(\delta)
\end{bmatrix}
, \ \ \vec{Y} = 
\begin{bmatrix}
\sin(\psi)\sin(h) - \cos(\psi)\cos(h)\sin(\delta) \\
\sin(\psi)\cos(h) + \cos(\psi)\sin(h)\sin(\delta) \\
\cos(\psi)\cos(\delta)
\end{bmatrix}
\end{align}

In the working Python implementation of RapidPE the computation of this quantity is serialized with respect to the samples. Our objective is to produce this quantity for a group of samples, all at once, as a coherent vectorized operation. One a sample-to-sample basis, the numbers that vary are the components of the vectors $\vec{X}$ and $\vec{Y}$. Thus we need a function that takes as input a \textit{list} vectors (or \textit{vector}) of vectors and produces a vector with the right components as output. To that end we define the tensor $X^{i}_{j}$ where

@@

\subsection{Vectorized Detector Arrival Time}

The use of the geocentric signal arrival time in the above computation of the complex antenna factors $F_+$ and $F_\times$ is equivalent to making the approximation that the detectors are all physically located at the geocenter (albeit maintaining their varying orientations). Here we present a vectorized method for computing the more realistic temporal offsets resulting from the physical placement of the detectors on the surface of the earth. Let $\mathbf{A} \circ \mathbf{B}$ denote the Hadamard product of tensors, defined such that

\begin{align}
C_{ij} = A_{ij}B_{ij} \equiv (\mathbf{A} \circ \mathbf{B})_{ij}
\end{align}

Given a vector $\vec{t_{geo}}$ the components of which are all exactly the Greenwich mean sidereal arrival time at geocenter, let $\vec{h} = \vec{t_{geo}} - \vec{\alpha}$ be a vector containing the conventionally defined hour angles for the samples in question, as well as vectors $\vec{\alpha}$ and $\vec{\delta}$ denoting the sample right ascensions and declinations respectively. The normal vector oriented in the sample source direction is then given by

\begin{align}
\vec{V_{s}} = 
\begin{bmatrix}
\cos(\vec{\delta}) \circ \cos(\vec{h}) \\
-\cos(\vec{\delta}) \circ \sin(\vec{h}) \\
\sin(\vec{\delta})
\end{bmatrix}
\end{align}

The above vector is relative to the standard celestial coordinate system for which the north pole is aligned along the $z$-axis and the $x$ axis points towards the Vernal equinox. In the same coordinate system, the vector pointing towards the detector in question $\vec{V_d}$ is available in a standard lookup table within the LAL software library. The sample arrival times $\vec{t_a}$ are then

\begin{align}
\vec{t_a} = \vec{t_{geo}} - \frac{1}{c}\vec{V_s} \cdot \vec{V_d}
\end{align}
